Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-07-08 WRITEUP/ms.tex
done conclusion

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
RXJ1131 is gravitationally lensed quasar.
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 a wet-merger, 
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
turbulent disk
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.

% In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
% grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
lying above 
the relation \citep[\eg][]{McLure06a,Peng06a}.
Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
While it has become clearer that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, 
such a picture is still unclear  at intermediate redshift.
This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected onto different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for the
relatively uncontaminated measurements of their emission.

\defcitealias{Sluse03a}{S03}
The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the 
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of radius 1\farcs83
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
We have thus carried out a detailed study for RXJ1131 as presented in this paper.
RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
The moderate mass black hole $M_{\rm BH}$\eq8\E{7}\Msun \citep{Sluse12a} %based on H beta line
residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,0.9;][]{Reis14a}, and
is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq1.3\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

This paper is structured as follows.
In \Sec{obs}, we outline the details of the observations and our data reduction process.
In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
and the resulting physical properties inferred for RXJ1131.
In \Sec{diss}, we discuss the merger stage of RXJ1131, and the implications of 
this study in the context of the evolution of molecular gas content
and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,230.5379938 GHz) redshifted to $\nu_{\rm obs}$\,=\,139.0\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this do not rely on this quantity.

@@

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS/Wide Field Camera 
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
The details of the observations can be found
in \citetalias{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth moment map, a red/blue channel map, and
the first and second moment maps in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are created using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity-integrated map.

@@

\subsection{\cco Emission}
We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent between \bco and \cco are similar and therefore
magnified by the same amount, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.

@@

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux
$S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy. Slightly extended emission is also detected
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

@@

The type of merger (major v.s. minor) in a pair of interacting galaxies 
is most commonly distinguished based on 
the ratio between their total galaxy mass.
Here, we use the gas mass ratio between RXJ1131 and
its companion galaxy instead, given that we do not have constraints on their individual galaxy mass.
We decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
derive its intrinsic gas mass using the best-fit flux 
densities and magnification factors obtained from the models of this channel.
Assuming a brightness temperature ratio 
of $r_{\rm 21}$\,=\,1 between \bco and \aco lines and
a CO luminosity-to-H$_2$ mass conversion factor of
\alphaco\,=\,0.8\,\alphaU, we find
a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun.
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun, which
implies a {\em gas} mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a {\em ``wet-wet'' minor merger}.
We caution that this is based on their gas mass ratio rather than their total galaxy mass ratio, which 
is more commonly used in literature as the
classification scheme to separate major mergers from minor mergers.

@@

\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
the virial-based black hole mass \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a} corresponds 
to a stellar bulge mass of $M_{\rm bulge}$\eq5.4\E{10}\,\Msun.
% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.83
This implies that the bulge component is responsible for making up $\sim$65\% of the dynamical mass. 
If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass. Since the dust mass only contributes a small fraction of the total mass, a factor of $\sim$2 difference is minor.}
from the dynamical mass and ignore a contribution from the dark matter, this would
yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
Thus, the bulge mass derived above based on the local relation is not unphysical.
The stellar mass upper limit would also imply a lower limit on the 
$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.12\%, which is consistent with the local relation within the scatter and with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
%Depending on the exact dark matter fraction, RXJ1131 may lie above the local $M_{\rm BH}$/$M_{\rm bulge}$.

>>>>

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
The spinning black hole in RXJ1131 is quadruply-imaged by a foreground galaxy at $z$\ssim0.3.
This is the first resolved \bco imaging at intermediate redshift.
We perform a dynamical lens modeling on the spatially and spectrally resolved \bco line emission.
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
turbulent disk
is indicative of, and suggests...
The lensing-corrected molecular gas of $M_{\rm gas}$\eq1.38\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
We thus conclude that RXJ1131 a wet minor merger.
Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun and a lensing-corrected \LIR\ssim1.5\E{12}\,\Lsun, corresponding to a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU . 
This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts. 
Dusty
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
%Demonstrate the first dynamical constraint on the MBH-sigma relation at intermediate redshift.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by 
a rapidly decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.

% In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
% grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
lying above 
the relation \citep[\eg][]{McLure06a,Peng06a}.
Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
While it has become clearer that high-$z$ galaxies deviate from the local relation, and among their galaxy populations, 
such a picture is still unclear  at intermediate redshift.
This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is being projected onto different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for the
relatively uncontaminated measurements of their emission.

\defcitealias{Sluse03a}{S03}
The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the 
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of radius $1$\farcs$83$
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
We have thus carried out a detailed study for RXJ1131 as presented in this paper.
RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
The moderate mass black hole $M_{\rm BH}$\eq$8$\E{7}\Msun \citep{Sluse12a} %based on H beta line
residing in RXJ1131 is rotating with a high spin parameter \citep[$a$\,$\sim$\,$0.9$;][]{Reis14a}, and
is radiating at an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

This paper is structured as follows.
In \Sec{obs}, we outline the details of the observations and our data reduction process.
In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
and the resulting physical properties inferred for RXJ1131.
In \Sec{diss}, we discuss the merger stage of RXJ1131, 
the scenario of a recoiling black hole, and the $M_{\rm BH}$$-$\mdyn relation.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.5379938$ GHz) redshifted to $\nu_{\rm obs}$\,=\,$139.0$\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
$21.5$ \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS/Wide Field Camera 
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
The details of the observations can be found
in \citetalias{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the high-resolution optical image.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth moment map, a red/blue channel map, and
the first and second moment maps in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are created using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

@@

\subsection{\cco Emission}
We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent between \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with 
thermalized excitation, as observed in other ULIRGs.

@@

We detect PdBI 2\,mm continuum in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux
$S_\nu$\,=\,800\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy. Slightly extended emission is also detected
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission toward
the background galaxy (RXJ1131).

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

@@

The type of merger (major v.s. minor) in a pair of interacting galaxies 
is most commonly distinguished based on 
the ratio between their total galaxy mass.
Here, we use the gas mass ratio between RXJ1131 and
its companion galaxy instead, given that we do not have stringent constraints on their individual galaxy mass.
We decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
derive its intrinsic gas mass using the best-fit flux 
densities and magnification factors obtained from the models of this channel.
Assuming a brightness temperature ratio 
of $r_{\rm 21}$\,=\,1 between \bco and \aco lines and
a CO luminosity-to-H$_2$ mass conversion factor of
\alphaco\,=\,0.8\,\alphaU, we find
a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun.
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun, which
implies a {\em gas} mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a {\em ``wet-wet'' minor merger}.
We caution that this is based on their gas mass ratio rather than their total galaxy mass ratio, which 
is more commonly used in literature as the
classification scheme to separate major mergers from minor mergers.

@@

\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
the virial-based black hole mass \mbh$\sim$\,8\E{7}\,\Msun \citep{Sluse12a} corresponds 
to a stellar bulge mass of $M_{\rm bulge}$\eq5.4\E{10}\,\Msun.
% \ie $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.15\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.83
This implies that the bulge component is responsible for making up $\sim$65\% of the dynamical mass. 
If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass. Since the dust mass only contributes a small fraction to the total mass, a factor of $\sim$2 difference is minor.}
from the dynamical mass and ignore a contribution from the dark matter, this would
yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
Thus, the bulge mass derived above based on the local relation is not unphysical.
The stellar mass upper limit would also imply a lower limit on the 
$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.12\%, which is consistent with the local relation within the scatter and with other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
%Depending on the exact dark matter fraction, RXJ1131 may lie above the local $M_{\rm BH}$/$M_{\rm bulge}$.
